Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-02 SWoPP2018 Paper/paper.tex
Changed the title and small additon of one extra data point.

\title{Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision}

@@

\section{Results}\label{sec:result}
The host (numpy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.

@@

\section{Conclusion}\label{sec:conclusion}
This framework makes for a good basis to start some research into different number formats.
CPU emulations of different formats reach very low performances.
So the expect to reach about similar performance on FPGA implementation using alternative floating point formats. %TODO Arthur performance metrics?

>>>>

\title{Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision}

@@

\section{Results}\label{sec:result}
The host (numpy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.
The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.

@@

\section{Conclusion}\label{sec:conclusion}
This framework makes for a good basis to start some research into different number formats.
CPU emulations of different formats reach very low performances.
Due to the FPGA's ability to use any numerical format that is required, the current implementation should not show the same performance degradation.
